---
title: "Shiny Application and Reproducible Pitch Assigment"
author: "Santosh Kumar"
date: "7/6/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Goal

This peer assessed assignment has two parts.First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Steps to Perform

### 1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
### 2. Deploy the application on Rstudio's shiny server
### 3. Share the application link by pasting it into the provided text box
### 4. Share your server.R and ui.R code on github

## How to use the application

Using the data provided by mtcars data set, we are trying to predict a car horsepower using two different linear model.

The application is running on (https://kumarsantosh0712.shinyapps.io/predictmodel/)

ui.R, and Server.R Code in my github repository (https://github.com/santoshkumar0712/Shiny_application)

## Plot
```{r plot, echo=FALSE, warning=FALSE}
plot(jitter(mtcars$hp) ~ mtcars$mpg,xlab="Car's MPG",ylab="HP",main="Cars MPG vs  HP",pch=19,frame.plot=FALSE,col=ifelse(mtcars$cyl > 4, "pink", "light blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.8)
```
